Reanalysis Step 2: Multiple Imputation

### 2025-08-17 reanalysis-2-multiple_imputation.qmd
dplyr error

# Summary of methods
final_methods <- data.frame(
  Variable = names(custom_methods),
  Method = custom_methods,
  Type = case_when(
    custom_methods == "" ~ "Predictor only (not imputed)",
    custom_methods == "pmm" ~ "Predictive mean matching",
    custom_methods == "polr" ~ "Proportional odds regression",
    custom_methods == "logreg" ~ "Logistic regression",
    custom_methods == "polyreg" ~ "Polytomous regression",
    TRUE ~ custom_methods
  )
) |>
  arrange(Method != "", Variable)

>>>>

# Summary of methods
method_types <- ifelse(custom_methods == "", "Predictor only (not imputed)",
                ifelse(custom_methods == "pmm", "Predictive mean matching",
                ifelse(custom_methods == "polr", "Proportional odds regression",
                ifelse(custom_methods == "logreg", "Logistic regression",
                ifelse(custom_methods == "polyreg", "Polytomous regression",
                       custom_methods)))))

final_methods <- data.frame(
  Variable = names(custom_methods),
  Method = custom_methods,
  Type = method_types,
  stringsAsFactors = FALSE
)

# Sort to show imputed variables first
final_methods <- final_methods[order(final_methods$Method == "", final_methods$Variable), ]
